R tools for accessing research literature for text mining

### 2019-08-23 manuscript.Rmd
fix #21 learn more about the pkgs at end of data sources section
fix #20 move case studies further up
fix #22 add section on papers that have used fulltext had to move use cases back down lower because really need to have talked about fulltext pkg first

# How to text mine from R: Three case studies

## Case study 1: Citation mining

>>>>

# Text mining in R: Use Cases

## Use cases in the literature

At least three papers have used the fulltext package. @Bauer2016 explored
a way to think about the qualitative impact of citations rather than simple
counts of citations; they did not use fulltext, but pointed it out as a good
option for collecting papers. @Walsh2018 used fulltext and [roadoi][], an
rOpenSci R package, to "map the literature" on nutritional interventions
in cognitive health. @Piper2019 in a review of DNA metabarcoding for
high-throughput insect surveillance used fulltext, along with [rentrez][]
(an rOpenSci package), to collect articles for text mining.

## Three case studies

The following three case studies demonstrate in brief how one could use
fulltext and related packages to do a few different text mining tasks.

### Case study 1: Citation mining

### 2019-08-23 manuscript.tex
fix #22 add section on papers that have used fulltext had to move use cases back down lower because really need to have talked about fulltext pkg first

\hypertarget{text-mining-in-r-three-case-studies}{%
\section{Text mining in R: Three case
studies}\label{text-mining-in-r-three-case-studies}}

\hypertarget{case-study-1-citation-mining}{%
\subsection{Case study 1: Citation
mining}\label{case-study-1-citation-mining}}

\hypertarget{case-study-2-abstract-mining}{%
\subsection{Case study 2: Abstract
mining}\label{case-study-2-abstract-mining}}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{kwic}\NormalTok{(corp, }\DataTypeTok{pattern =} \StringTok{"ecology"}\NormalTok{)}
\CommentTok{#>                                                                         }
\CommentTok{#>   [text1, 33] knowledge production within critical political | ecology |}
\CommentTok{#>   [text1, 50]              in scientific articles on dryland | ecology |}
\CommentTok{#>  [text1, 204]                 to equilibrium models in range | ecology |}
\CommentTok{#>  [text1, 246]    communal areas.Keywords: Critical political | ecology |}
\CommentTok{#>  [text1, 255]                 , scientific models, rangeland | ecology |}
\CommentTok{#>    [text2, 5]                            < jats:p> Political | ecology |}
\CommentTok{#>   [text2, 23]        manifestations of political economy and | ecology |}
\CommentTok{#>   [text2, 45]                      I try to extend political | ecology |}
\CommentTok{#>  [text2, 149]                   , in dialogue with political | ecology |}
\CommentTok{#>  [text2, 177]            people and resources that political | ecology |}
\CommentTok{#>  [text2, 229]      indigeneity scholars.Key words: political | ecology |}
\CommentTok{#>   [text3, 71]                   an analysis from a political | ecology |}
\CommentTok{#>  [text3, 114]                system, supermarkets, political | ecology |}
\CommentTok{#>  [text6, 134]                was observed when allopatry and | ecology |}
\CommentTok{#>  [text7, 167]             ecosystem should be considered for | ecology |}
\CommentTok{#>  [text7, 185]                       the" four-color issue of | ecology |}
\CommentTok{#>  [text7, 201]             step toward advancing knowledge in | ecology |}
\CommentTok{#>  [text9, 195]         or for theoretical studies integrating | ecology |}
\CommentTok{#>                                              }
\CommentTok{#>  . This article is a                         }
\CommentTok{#>  , and investigates the functions            }
\CommentTok{#>  , and the fence-line photographs            }
\CommentTok{#>  , fence-line photography, scientific        }
\CommentTok{#>  , Southern Africa</                         }
\CommentTok{#>  has expanded in multiple new                }
\CommentTok{#>  in the" problem"                            }
\CommentTok{#>  to engage with ethnic studies               }
\CommentTok{#>  approaches to better understand the         }
\CommentTok{#>  focuses on cannot be adequately             }
\CommentTok{#>  , coloniality, Maidu,                       }
\CommentTok{#>  standpoint allows a different interpretation}
\CommentTok{#>  </ jats:p>                                  }
\CommentTok{#>  act together, leading to                    }
\CommentTok{#>  "? Here, I                                  }
\CommentTok{#>  ", and propose that                         }
\CommentTok{#>  and conservation biology. In                }
\CommentTok{#>  and biogeography.</}
\end{Highlighting}
\end{Shaded}

\hypertarget{case-study-3-full-text-mining}{%
\subsection{Case study 3: Full text
mining}\label{case-study-3-full-text-mining}}

@@

@@

@@

@@

>>>>

@@

\hypertarget{text-mining-in-r-use-cases}{%
\section{Text mining in R: Use Cases}\label{text-mining-in-r-use-cases}}

\hypertarget{use-cases-in-the-literature}{%
\subsection{Use cases in the
literature}\label{use-cases-in-the-literature}}

At least three papers have used the fulltext package. Bauer, Barbera \&
Munzert (2016) explored a way to think about the qualitative impact of
citations rather than simple counts of citations; they did not use
fulltext, but pointed it out as a good option for collecting papers.
Walsh \& Cherbuin (2018) used fulltext and
\href{https://github.com/ropensci/roadoi}{roadoi}, an rOpenSci R
package, to ``map the literature'' on nutritional interventions in
cognitive health. Piper et al. (2019) in a review of DNA metabarcoding
for high-throughput insect surveillance used fulltext, along with
\href{https://github.com/ropensci/rentrez}{rentrez} (an rOpenSci
package), to collect articles for text mining.

\hypertarget{three-case-studies}{%
\subsection{Three case studies}\label{three-case-studies}}

The following three case studies demonstrate in brief how one could use
fulltext and related packages to do a few different text mining tasks.

\hypertarget{case-study-1-citation-mining}{%
\subsubsection{Case study 1: Citation
mining}\label{case-study-1-citation-mining}}

\hypertarget{case-study-2-abstract-mining}{%
\subsubsection{Case study 2: Abstract
mining}\label{case-study-2-abstract-mining}}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{kwic}\NormalTok{(corp, }\DataTypeTok{pattern =} \StringTok{"ecology"}\NormalTok{, }\DataTypeTok{window =} \DecValTok{2}\NormalTok{)}
\CommentTok{#>                                                                }
\CommentTok{#>   [text1, 33]  critical political | ecology | . This           }
\CommentTok{#>   [text1, 50]          on dryland | ecology | , and            }
\CommentTok{#>  [text1, 204]            in range | ecology | , and            }
\CommentTok{#>  [text1, 246]  Critical political | ecology | , fence-line     }
\CommentTok{#>  [text1, 255]         , rangeland | ecology | , Southern       }
\CommentTok{#>    [text2, 5]         > Political | ecology | has expanded     }
\CommentTok{#>   [text2, 23]         economy and | ecology | in the           }
\CommentTok{#>   [text2, 45]    extend political | ecology | to engage        }
\CommentTok{#>  [text2, 149]      with political | ecology | approaches to    }
\CommentTok{#>  [text2, 177]      that political | ecology | focuses on       }
\CommentTok{#>  [text2, 229]         : political | ecology | , coloniality    }
\CommentTok{#>   [text3, 71]         a political | ecology | standpoint allows}
\CommentTok{#>  [text3, 114]         , political | ecology | </               }
\CommentTok{#>  [text6, 134]       allopatry and | ecology | act together     }
\CommentTok{#>  [text7, 167]      considered for | ecology | "?               }
\CommentTok{#>  [text7, 185]            issue of | ecology | ",               }
\CommentTok{#>  [text7, 201]        knowledge in | ecology | and conservation }
\CommentTok{#>  [text9, 195] studies integrating | ecology | and biogeography}
\end{Highlighting}
\end{Shaded}

\hypertarget{case-study-3-full-text-mining}{%
\subsubsection{Case study 3: Full text
mining}\label{case-study-3-full-text-mining}}

@@

\leavevmode\hypertarget{ref-Bauer2016}{}%
Bauer PC., Barbera P., Munzert S. 2016. The quality of citations:
Towards quantifying qualitative impact in social science research.
\emph{SSRN Electronic Journal}.

@@

\leavevmode\hypertarget{ref-Piper2019}{}%
Piper AM., Batovska J., Cogan NOI., Weiss J., Cunningham JP., Rodoni
BC., Blacket MJ. 2019. Prospects and challenges of implementing DNA
metabarcoding for high-throughput insect surveillance.
\emph{GigaScience} 8.

@@

\leavevmode\hypertarget{ref-Walsh2018}{}%
Walsh E., Cherbuin N. 2018. Mapping the literature on nutritional
interventions in cognitive health: A data-driven approach.
\emph{Nutrients} 11:38.
